### 2020-03-17 paper/main.tex
typo

Given that this dataset is ten times larget than our other two datasets, we wanted to try different training and test splits, going as low as 8\% for training data and using the remaining 92\% as test data. We ran the same number of cross-validations as our previous tests and found minimal difference in performance.

>>>>

Given that this dataset is ten times larger than our other two datasets, we wanted to try different training and test splits, going as low as 8\% for training data and using the remaining 92\% as test data. We ran the same number of cross-validations as our previous tests and found minimal difference in performance.
